### 2023-11-27 results/main/13explicitIgnorance/models/analysis1/table1.tex
updated naturalness paper analysis and paper

 continue & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  too & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  also & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  again & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  stop & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  \color{orange}be annoyed\color{black} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  cleft & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  \color{orange}know\color{black} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  \color{green}demonstrate\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}pretend\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}inform\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}confess\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{orange}see\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}acknowledge\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{orange}discover\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}admit\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}hear\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}prove\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{orange}reveal\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}announce\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} \\ 
  \color{green}be right\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}establish\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} \\ 

>>>>

 {\bf continue} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  {\bf too} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  {\bf also} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  {\bf again} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  {\bf stop} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  \color{orange}{\bf be annoyed}\color{black} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  {\bf cleft} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  \color{orange}{\bf know}\color{black} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow1} & \cellcolor{yellow1} \\ 
  \color{green}{\bf demonstrate}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf pretend}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf inform}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf confess}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{orange}{\bf see}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf acknowledge}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{orange}{\bf discover}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf admit}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf hear}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf prove}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{orange}{\bf reveal}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf announce}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} \\ 
  \color{green}{\bf be right}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{white} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} & \cellcolor{yellow2} \\ 
  \color{green}{\bf establish}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{white} & \cellcolor{white} & \cellcolor{black} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow3} & \cellcolor{yellow2} \\ 
  \color{green}{\bf confirm}\color{black} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple1} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple2} & \cellcolor{purple2} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{purple3} & \cellcolor{black} & \cellcolor{white} & \cellcolor{white} & \cellcolor{yellow3} \\ 
